A Hitchhiker's Guide to Reproducible Research" # replace with something serious

### 2021-01-26 manuscript.Rmd
cite lavaan

---
title: "A Hitchhiker's Guide to Reproducible Research" # replace with something serious
output: bookdown::pdf_document2
repro:
  packages:
    - usethis
    - repro
    - here
csl: apa7.csl
bibliography: references.bib
---

@@

It is probably better to assume values that are more pessimistic.
Instead of taking these values as they are we will therefore assume that the loadings are 30% lower than reported and that the standardized mean difference is only 0.1.
These assumption can be simply translated into `lavaan` model syntax:

>>>>

---
title: "A Hitchhiker's Guide to Reproducible Research" # replace with something serious
output: bookdown::pdf_document2
repro:
  packages:
    - usethis
    - repro
    - here
csl: apa7.csl
bibliography: ["references.bib", "packages.bib"]
---

@@

It is probably better to assume values that are more pessimistic.
Instead of taking these values as they are we will therefore assume that the loadings are 30% lower than reported and that the standardized mean difference is only 0.1.
These assumption can be simply translated into [`lavaan` [@lavaan]](https://lavaan.ugent.be)[^lavaan] model syntax:

[^lavaan]: https://lavaan.ugent.be
